Codebook
========
This codebook is created with great references from this github link.
https://github.com/benjamin-chan/GettingAndCleaningData

Variable list and descriptions
------------------------------

Variable name    | Description
-----------------|------------
Subject          | ID the subject who performed the activity for each window sample. Its range is from 1 to 30.
ActivityName     | Activity name
Domain           | Feature: Time domain signal or frequency domain signal (Time or Freq)
Instrument       | Feature: Measuring instrument (Accelerometer or Gyroscope)
Acceleration     | Feature: Acceleration signal (Body or Gravity)
Variable         | Feature: Variable (Mean or SD)
Jerk             | Feature: Jerk signal
Magnitude        | Feature: Magnitude of the signals calculated using the Euclidean norm
Axis             | Feature: 3-axial signals in the X, Y and Z directions (X, Y, or Z)
Count            | Feature: Count of data points used to compute `average`
Avg              | Feature: Average of each variable for each activity and each subject

Dataset structure
-----------------

```{r}
str(tidyData)
```

List the key variables
----------------------------------------

```{r}
key(tidyData)
```

Head of data set
------------------------------

```{r}
head(tidyData)
```

Summary of variables
--------------------

```{r}
summary(tidyData)
```

Save to file
------------

```{r save}
f <- file.path(path, "tidy-UCI-HAR-Dataset.txt")
write.table(tidyData, f, row.names=FALSE)
```
